Abstract Binding Trees

### 2015-10-25 paper.tex
remove silly statement

Because we have not committed to using the built-in binding machinery to
express the well-scopedness of telescopes and sequents, we are free to use
\emph{symbols} in order to model the variables in the context. This is in fact
quite sensible if we are actually trying to faithfully represent the syntax of
telescopes and sequents, rather than replace them with their counterparts on
the meta-level. It is certainly not intended that we should be able to take a
context $\Match{H}{x:A}$ and apply the substitution $\IsSubst{M}{x}{H}{M:A}$,
which is nonsensical; on the other hand, if $x$ had been a \emph{symbol}, all
we could do is rename it in the context, since substitution is not defined for
symbols.

>>>>

Because we have not committed to using the built-in binding machinery to
express the well-scopedness of telescopes and sequents, we are free to use
\emph{symbols} in order to model the variables in the context. This is in fact
quite sensible if we are actually trying to faithfully represent the syntax of
telescopes and sequents, rather than replace them with their counterparts on
the meta-level.
